### 2022-05-30 article.tex
Add refs

\begin{table}[h]
  \begin{tabular}{lll}
    Term      & Definition                                            & Example                                                         \\
    \hline
    Data      & Individual facts, statistics, or items of information & A SNP that has a significant association                        \\
    Genotype  & The DNA allele at a certain location                  & AA, AC, CG, GT, ...                                             \\
    Paradata  & Data that describes the generation of data            & The code to conclude that a SNP has a significant association   \\
    Phenotype & How an organism looks like in the broadest sense      & The concentration of IL6RA in the blood                         \\
    Metadata  & Data that provides information about other data       & The article that describes an experiment                        \\
    Trait     & A phenotype                                           & The concentration of IL6RA in the blood                         
  \end{tabular}
\end{table}

@@

The simplest metric to assess the quality of code is 
the amount of (single) lines of code (SLOC). 
Code that has a lower SLOC count, i.e. it is more concise,
is usually regarded as having a lower chance of containing bugs.

@@

There are multiple websites for hosting code, with GitHub,
and GitLab being the most well-known.
GitHub is the most commonly used website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

A commit history helps to assess the honesty 
in the reporting of the code. 
Ideally, the full version history of the code 
has been generated, by hosting the code directly at its inception.
However, in some repositories, only the final version of the code has been
posted, which means all historical information is lost.
From a code history, it can be observed, for example, 
how much statistical tests have really/actually been done 
and see if all are reported:
not reporting a statistical tests is considered a Dubious Research Practice 
\richel{REF}, as this allows dishonest reporting of p-value hacking.

@@

Some code hosts, among others, GitHub, 
allows the researcher to start software scripts when uploading a new version.
To determine the reproducibility of the code, one such script should
run the code (on trivial data) to verify if the code works at all.
If the functionality of the code is lost, the researcher
can immediatly see which small change was the cause of this.
A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. The higher the code coverage,
the \richel{ref}.

@@

This article and its metadata can be found at 
\url{https://github.com/richelbilderbeek/chapter_paradata}.

>>>>

\begin{table}[h]
  \begin{tabular}{lll}
    Term      & Definition                                            & Example                                                         \\
    \hline
    Code      & Body of text to be run by a computer                  & The scripts run by a computational experiment                   \\
    Data      & Individual facts, statistics, or items of information & A SNP that has a significant association                        \\
    Genotype  & The DNA allele at a certain location                  & AA, AC, CG, GT, ...                                             \\
    Paradata  & Data that describes the generation of data            & The code to conclude that a SNP has a significant association   \\
    Phenotype & How an organism looks like in the broadest sense      & The concentration of IL6RA in the blood                         \\
    Metadata  & Data that provides information about other data       & The article that describes an experiment                        \\
    Trait     & A phenotype                                           & The concentration of IL6RA in the blood                         
  \end{tabular}
\end{table}

@@

The simplest metric to assess the quality of code is 
the amount of (single) lines of code (SLOC). 
Code that has a lower SLOC count, i.e. it is more concise,
is usually regarded as having a lower chance of containing bugs.
Additionally, following a style guide (e.g. \cite{style_guide}), 
improves software quality (\cite{fang2001}).

@@

There are multiple websites for hosting code, with GitHub,
and GitLab being the most well-known.
GitHub is the most commonly used website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
The use of code hosting websites, such as GitHub,
accommodates collaboration (\cite{perez2016ten}).
\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
and improves transparency (\cite{gorgolewski2016practical}).
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

Hosted code improves transparency (\cite{gorgolewski2016practical}).
The history of changes, called the commit history, 
helps to assess the honesty in the reporting of the code. 
Ideally, the full version history of the code 
has been generated, by hosting the code directly at its inception.
However, in some repositories, only the final version of the code has been
posted, which means all historical information is lost.
From a code history, it can be observed, for example, 
how much statistical tests have really/actually been done 
and see if all are reported:
not reporting a statistical tests is considered a Dubious Research Practice 
\richel{REF}, as this allows dishonest reporting of p-value hacking.

@@

Some code hosts, among others, GitHub, 
allows the researcher to start software scripts when uploading a new version.
To determine the reproducibility of the code, one such script should
run the code (on trivial data) to verify if the code works at all.
If the functionality of the code is lost, the researcher
can immediatly see which small change was the cause of this.
A formalized version of this workflow is called continuous integration (CI).
Using a CI service (such as GitHub Actions), is known to significantly 
increase the number of bugs exposed (\cite{vasilescu2015}) and increases
the speed at which new features are added (\cite{vasilescu2015}).

A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. Code coverage
correlates with code quality (\cite{horgan1994,del1995correlation}).

@@

This article and its metadata can be found at 
\begin{sloppypar}\url{https://github.com/richelbilderbeek/chapter_paradata}\end{sloppypar}.
